Data Preparation

### 2021-06-24 paper.Rmd
initial stab after loops

```{r}
#Reading raw data

@@

```{r}
#Joining to ADEP
fb2 <- left_join(fb1, apt_countries, by = c("ADEP" = "ICAO")) %>% mutate(ADEP_CTRY = CTRY, .keep = "unused", .after = ADEP)
#Joining to ADES
fb3 <- left_join(fb2, apt_countries, by = c("ADES" = "ICAO")) %>% mutate(ADES_CTRY = CTRY, .keep = "unused", .after = ADES)

@@

```{r}
#quick peek
base_dataset
#
#
#
#NOW IT'S TIME TO LOOP TO OTHER MONTHS AND BIND THEM ALL!
#
#
#
```

```{r}
#quick first look
temp1 <- base_dataset %>% group_by(DATE, ADEP_REG, ADES_REG) %>% summarize(FLIGHTS = n(), .groups = "drop") %>%
  filter(ADEP_REG %in% c("BR", "EU"), ADES_REG  %in% c("BR", "EU")) %>%
  mutate(ROUTE = paste(ADEP_REG, ADES_REG, sep = "-"), .keep = "unused", .before = "FLIGHTS") %>%
  pivot_wider(names_from = ROUTE, values_from = FLIGHTS) 
temp1

@@

#Normalized by the median of the last 3 months of the dataset
temp2 <- temp1 %>% pivot_longer(cols = 2:5, names_to = "ROUTE", values_to = "FLIGHTS") %>% group_by(ROUTE) %>% mutate(MOVING_MEDIAN = quantile(FLIGHTS[month(DATE) %in% month(last(DATE))-2:month(last(DATE))], probs = 0.5), NORM_FLTS = FLIGHTS/MOVING_MEDIAN)
temp2

>>>>

```{r eval=FALSE, include=FALSE}
#Reading raw data

@@

```{r, eval=FALSE, include=FALSE}
#Joining to ADEP
fb2 <- left_join(fb1, apt_countries, by = c("ADEP" = "ICAO")) %>% mutate(ADEP_CTRY = CTRY, .keep = "unused", .after = ADEP)
#Joining to ADES
fb3 <- left_join(fb2, apt_countries, by = c("ADES" = "ICAO")) %>% mutate(ADES_CTRY = CTRY, .keep = "unused", .after = ADES)

@@

```{r}
#quick peek
#Read "x0_data-preparation.Rmd" first, then
full_dataset

temp <- full_dataset %>% group_by(DATE, ADEP_REG, ADES_REG) %>% summarize(FLIGHTS = n(), .groups = "drop") %>%
  filter(ADEP_REG %in% c("BR", "EU"), ADES_REG  %in% c("BR", "EU")) %>%
  mutate(ROUTE = paste(ADEP_REG, ADES_REG, sep = "-"), .keep = "unused", .before = "FLIGHTS") %>%
  pivot_wider(names_from = ROUTE, values_from = FLIGHTS) 
temp

#First Look
temp1 <- full_dataset %>% group_by(DATE, ADEP_REG, ADES_REG) %>% summarize(FLIGHTS = n()) %>% mutate(ROUTE = paste(ADEP_REG, ADES_REG, sep = "-"), .keep = "unused")
temp1

temp1 %>% ggplot(aes(x = DATE)) +
  geom_line(aes(y = (FLIGHTS), color = ROUTE))

@@

#Normalized by the median of the last 3 months of the dataset
temp1 %>% pivot_longer(cols = 2:5, names_to = "ROUTE", values_to = "FLIGHTS") %>% group_by(ROUTE) %>%
  mutate(MOVING_MEDIAN = quantile(FLIGHTS[month(DATE) %in% month(last(DATE))-2:month(last(DATE))], probs = 0.5), NORM_FLTS = FLIGHTS/MOVING_MEDIAN)
temp2

### 2021-06-24 x0_data-preparation.Rmd
initial stab after loops

```{r, eval=FALSE}
#quick peek
base_dataset
#
#
#
#NOW IT'S TIME TO LOOP TO OTHER MONTHS AND BIND THEM ALL!
#
#
#

#quick first look
temp1 <- base_dataset %>% group_by(DATE, ADEP_REG, ADES_REG) %>% summarize(FLIGHTS = n()) %>% mutate(ROUTE = paste(ADEP_REG, ADES_REG, sep = "-"), .keep = "unused")

>>>>

```{r, eval=TRUE}
#quick peek

base_filenames <- list.files("./data/", pattern = "base_osn_*")
base_fullnames <- c(paste0("./data/", base_filenames))
full_dataset <- map_dfr(base_fullnames, read_csv)

```{r}
#quick first look
temp1 <- full_dataset %>% group_by(DATE, ADEP_REG, ADES_REG) %>% summarize(FLIGHTS = n()) %>% mutate(ROUTE = paste(ADEP_REG, ADES_REG, sep = "-"), .keep = "unused")
temp1
